\bf Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-01-25 nips2015.tex
better .tex

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{qtree}
\usepackage{natbib}
\usepackage{graphicx}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

@@

\title{Primal-dual algorithm for computing Nash equilibria in
% two-person zero-sum
sequential games with imcomplete information
% with imcomplete information and perfect recall
}

@@

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games with imcomplete information and perfect-recall like Texas Hold'em Poker, which converges after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external first-order oracles, etc.). %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequen e-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to compute Nash equilibria for the games considered here since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
Our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent problem which is amendable to the primal-dual scheme, without any additional overhead. The resulting algorithm is simple (less than 10 lines of code), only involving matvec (matrix-vector multiplication) and clipping. The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

@@

\begin{remark}  
  Even though problem \eqref{eq:primal_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
\end{remark}

@@

\subsection{Statement of the problem}
Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria

@@

\subsection{Outline of the article}
In section \ref{sec:rep} we briefly review the sequence-form representation. In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria. Section \ref{sec:notation} features useful notions of convex optimization (proximal operators, convex conjugates, etc.). In section \ref{sec:algo} we derive the proposed algorithm for producing a NAsh $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate. We conclude with a demonstration on Kuhn 3-card Poker \cite{kuhn}.

@@

\section{The sequence-form representation}
\label{sec:rep}
In this section, we briefly recall the sequence-form representation of sequential games with imcomplete information and perfect recall. A complete overview of the subject can be found in the pioneering work \cite{von1996efficient}.

\subsection{The Game tree}
The game tree $\mathcal{T}$ is defined as follows. There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically. Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{strategic-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

$a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
We will assume implicitly that each (non-chance) player is rational.

\subsection{Player sequences}
For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

\subsection{Pure strategies, mixed strategies, realization plans}
Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$ (i.e the prescription of a move $c \in C_h$ from each information set $h \in \mathcal{I}_k$), and their \textit{mixed-strategies} are randomizations on these pure-strategies. A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts. The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.

The strategy profile of player $k$ is then the set of $n_k$-dimensional vectors $z$ satisfying
% Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
\begin{equation}
  z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0, \hspace{1em} \forall h \in \mathcal{I}_k
  \label{eq:lin}
\end{equation}

These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$, and so the polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.

\subsection{Behavioral strategies}
Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
\begin{equation}
  \beta_k(h, c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}

From this definition, it is clear that each behavioral-strategy is equivalent to a mixed-strategy.

\subsection{Payoff matrix}
The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
\begin{equation}
    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \hspace{1em} \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
  \end{equation}

If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.

\subsection{What matters}
The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games. However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.

\subsection{Example: Sequence-form representation of Kuhn Poker}
\label{sec:kuhn_sf}
The Kuhn 3-card Poker \cite{kuhn} has sequence-form specification given by (not showing zero entries)\\
$A = \left[\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right]$,\\
$E_1 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
and $E_2 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right]$.\\

\section{Useful convex analysis}
\label{sec:notation}
We will need the following notations in the sequel. The passionate reader should refer to the classic \cite{rockafellar1997convex} for a more elaborate presentation.

\subsection{Linear algebra, nonnegative clipping, indicator functions, euclidean projection}
Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional orthant.  For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
$(x)_+$ denotes its point-wise maximum with 0, an operation referred to a \textit{nonnegative-clipping}. Note that $(x)_+ \in \mathbb{R}^n_+$.
For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).

@@

\section{Related work}
In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form

\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
  \label{eq:gilpin}
\end{equation}

They authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.

In \cite{gilpinfirst}, a modified verson of the technqiues in \cite{hoda2010smoothing} was developed. The authors proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}). Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain \textit{condition number} for the given game.
It should be noted however that though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small. Most importantly, the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle. Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.

@@

@@

More recently, \cite{chambolle2014ergodic} employs the primal-dual algorithm was applied to matrix games on simplexes. It should be stressed that such matrix games are considerably simpler than the games considered here. Indeed, the authors in \cite{chambolle2014ergodic} use the fact that computing the euclidean projection of a point unto a simplex can be done in linear time \cite{duchi2008efficient}, in contrast to the polytopes $Q_k$ defined in \eqref{eq:polytope} for which no such efficient algorithm is known nor is likely to exist. Note that computing the euclidean projection of a point unto the polytope $Q_k$ can still be done iteratively using the algorithm in proposition 4.2 of \cite{combettes2010dualization}, for example. However, the authors didn't provide a convergence rate for their algorithm, and as with any nested iterative scheme, one would have to solve this sub-problem with finer and finer precision.

@@

\subsection{Unconstrained minimax reformulation of the problem}
It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$. Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty.

@@

and the p.c.l.s.c functions $G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow (-\infty, +\infty]$ and $G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ are defined by
  \begin{equation}
      G_1(y, p) := i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1, \hspace{1em} G_2(x, q) := i_{\mathbb{R}^{n_1}_+}(x) + q^Te_2
    \label{eq:things}
  \end{equation}

@@

\section{Results}
To access the practical quality of the proposed algorithm, we experimented it on real and simulated games. The results are presented here.

>>>>

\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{color}

%% \documentclass{article} % For LaTeX2e
%% \usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{qtree}
\usepackage{natbib}
\usepackage{graphicx}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

@@

\title{\bf Primal-dual algorithm for computing Nash equilibria in
% two-person zero-sum
sequential games with imcomplete information
% with imcomplete information and perfect recall
}

@@

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect-recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external first-order oracles, etc.). %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequen e-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010, chambolle2014ergodic}. It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the afore-mentioned games considered here since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point convex-convex problem which is amendable to the primal-dual scheme (i.e all proximal operators can be computed in closed-form). Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

@@

\begin{remark}  
It should be noted that even though problem \eqref{eq:primal_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
\end{remark}

@@

\subsection{Statement of the problem}
Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria.

@@

\subsection{Outline of the article}
 Section \ref{sec:notation} exposes useful notions of convex optimization (proximal operators, convex conjugates, etc.) which will be crucial for the sequel. In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria. In section \ref{sec:algo} we derive the proposed algorithm for producing a NAsh $\epsilon$-equilibrium and prove its $\mathcal{O}(1/\epsilon)$ convergence rate. Section \ref{sec:results} presents practical results obtained both on simulated matrix games and the Kuhn 3-card Poker \cite{kuhn}.

@@

%% \section{The sequence-form representation}
%% \label{sec:rep}
%% In this section, we briefly recall the sequence-form representation of sequential games with imcomplete information and perfect recall. A complete overview of the subject can be found in the pioneering work \cite{von1996efficient}.

%% \subsection{The Game tree}
%% The game tree $\mathcal{T}$ is defined as follows. There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically. Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
%% The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{strategic-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
%% At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

%% $a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
%% receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
%% The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
%% We will assume implicitly that each (non-chance) player is rational.

%% \subsection{Player sequences}
%% For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices from the root node, to $h$ (i.e to any node in $h$), ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
%% \begin{equation}
%% \mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
%% \end{equation}
%% Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
%% $\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

%% \subsection{Pure strategies, mixed strategies, realization plans}
%% Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$ (i.e the prescription of a move $c \in C_h$ from each information set $h \in \mathcal{I}_k$), and their \textit{mixed-strategies} are randomizations on these pure-strategies. A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts. The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.

%% The strategy profile of player $k$ is then the set of $n_k$-dimensional vectors $z$ satisfying
%% % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
%% \begin{equation}
%%   z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
%%     z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0, \hspace{1em} \forall h \in \mathcal{I}_k
%%   \label{eq:lin}
%% \end{equation}

%% These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
%% where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$, and so the polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}.

%% \subsection{Behavioral strategies}
%% Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioral-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
%% \begin{equation}
%%   \beta_k(h, c) := \begin{cases}
%%     z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
%%     0, &\mbox{Otherwise}.
%%   \end{cases}
%% \end{equation}

%% From this definition, it is clear that each behavioral-strategy is equivalent to a mixed-strategy.

%% \subsection{Payoff matrix}
%% The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
%% \begin{equation}
%%     A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \hspace{1em} \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
%%   \end{equation}

%% If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.

%% \subsection{In summary}
%% The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games. However, since we are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.

%% \subsection{Example: Sequence-form representation of Kuhn Poker}
%% \label{sec:kuhn_sf}
%% The Kuhn 3-card Poker \cite{kuhn} has sequence-form specification given by (not showing zero entries)\\
%% $A = \left[\begin{array}{ccccccccccccc}
%%   &   &   &   &   &   &   &   &   &   &   &   &  \\
%%   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
%%   &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
%%   &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
%%   &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
%%   &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
%%   &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
%%   &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
%%   & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
%%   &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
%%   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
%%   &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
%%   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
%% \end{array}\right]$,\\
%% $E_1 = \left[\begin{array}{ccccccccccccc}
%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
%% -1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
%% -1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
%% -1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
%%   & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
%%   &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
%%   &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
%% \end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
%% and $E_2 = \left[\begin{array}{ccccccccccccc}
%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
%% -1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
%% -1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
%% -1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
%% -1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
%% -1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
%% -1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
%% \end{array}\right]$.\\

\section{Useful convex analysis}
\label{sec:notation}
We will need the following notations in the sequel. The passionate reader should refer to the classic \cite{rockafellar1997convex} for a more elaborate presentation. This section can be omitted without loss of continuity.

\subsection{Linear algebra, nonnegative clipping, indicator functions, euclidean projection}
Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional orthant.  For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
$(x)_+:=\text{max}(0, x)$ is the point-wise maximum of $x$ with 0. $(.)_+$ is the well-known (multi-dimensional) \textit{ramp} function.For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).

@@

\section{Related work}
\label{sec:related_work}
We present a selection of algorithms that is representative of the efforts that have been made in the literature to compute Nash $\epsilon$-equilibria for two-person zero-sum games with imcomplete information like Texas Hold'em Poker, etc.

In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form

\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
  \label{eq:gilpin}
\end{equation}
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate (which derives from the general EGT theory) for the outer-most iteration loop, though the cost of an iteration is presumably heavy since it entails computing a $softmax$ at each iteration.

In \cite{gilpinfirst}, a modified verson of the technqiues in \cite{hoda2010smoothing} was developed. The authors proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}). Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain \textit{condition number} for the given game.
It should be noted however that
\begin{itemize}
\item[--] Though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small.
\item[--] Most importantly, the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle. Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
\end{itemize}

@@

The primal-dual algorithm first developed in \cite{chambolle2010}, was proposed \cite{chambolle2014ergodic} to solve matrix games on simplexes. It should be stressed that such matrix games are considerably simpler than the games considered here. Indeed, the authors in \cite{chambolle2014ergodic} use the fact that computing the euclidean projection of a point unto a simplex can be done in linear time \cite{duchi2008efficient}, in contrast to the polytopes $Q_k$ defined in \eqref{eq:polytope} for which no such efficient algorithm is known nor is likely to exist. Note that computing the euclidean projection of a point unto the polytope $Q_k$ can still be done iteratively using the algorithm in proposition 4.2 of \cite{combettes2010dualization}, for example. However, the authors didn't provide a convergence rate for their algorithm, and as with any nested iterative scheme, one would have to solve this sub-problem with finer and finer precision.

@@

@@

\subsection{Unconstrained minimax reformulation of the problem}
It should be noted that the difficulty of applying the general primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to problem \eqref{eq:primal_pb} lies in the difficulty of effectively computing the euclidean projections $\Pi_{Q_k}$. Theorem \ref{thm:pd} provides a trick to effectively evade this difficulty, by re-writting the problem into an equivalent saddle-point convex-concave problem for which the associated proximal operators are simple.

@@

and the p.c.l.s.c functions $G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow (-\infty, +\infty]$ and \\$G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ are defined by
  \begin{equation}
      G_1(y, p) := i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1, \hspace{1em} G_2(x, q) := i_{\mathbb{R}^{n_1}_+}(x) + q^Te_2
    \label{eq:things}
  \end{equation}

@@

\section{Results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we experimented it on real and simulated games. The results are presented here.
